\LARGE BAND\\ \Large Unleashing Tokenized Economy

### 2018-03-17 paper.tex
Bump version: 0.1.2
Add Roadmap

\title{\LARGE BAND\\
    \Large Unleashing Tokenized Economy}
\author{
        Soravis Srinawakoon\\
        \small\href{mailto:soravis@bandprotocol.com}
            {\nolinkurl{soravis@bandprotocol.com}}
    \and
        Sorawit Suriyakarn\\
        \small\href{mailto:swit@bandprotocol.com}
            {\nolinkurl{swit@bandprotocol.com}}
    }
\date{\today\\\small Draft Version 0.1.1}
\begin{document}

@@

>>>>

\title{\LARGE BAND\\
    \Large Unleashing Tokenized Economy}
\author{
        Soravis Srinawakoon\\
        \small\href{mailto:soravis@bandprotocol.com}
            {\nolinkurl{soravis@bandprotocol.com}}
    \and
        Sorawit Suriyakarn\\
        \small\href{mailto:swit@bandprotocol.com}
            {\nolinkurl{swit@bandprotocol.com}}
    }
\date{\today\\\small Draft Version 0.1.2}
\begin{document}

@@

BAND Protocol has been conceived and been in active development since 2017. The following is our roadmap from ideation to our working product. Note that this is a targeted roadmap and may be subjected to change due to uncertainty in software development process.

\paragraph{Q3 - Q4 2017}
\begin{itemize}
\itemsep0em
\item Concept development
\item Research into crypto-primitives and technology
\item Market validation with real artists
\item Prototype different blockchain consensus protocol
\end{itemize}
\paragraph{Q1 2018}
\begin{itemize}
\itemsep0em
\item Draft whitepaper and go-to-market strategy
\item Draft yellowpaper
\item Begin product development
\end{itemize}
\paragraph{Q2 2018}
\begin{itemize}
\itemsep0em
\item Publish papers for peer-review
\item Launch our website
\item Launch our social media presence
\end{itemize}
\paragraph{Q3 2018}
\begin{itemize}
\itemsep0em
\item Launch testnet
\item Initiate bounty program
\item Initiate marketing campaign
\item Expand business partnership
\end{itemize}
\paragraph{Q4 2018}
\begin{itemize}
\itemsep0em
\item Launch first version of BAND Protocol with mainnet release
\item Launch Campbase with business partners and gather feedback
\item Publish official developer guidelines
\end{itemize}
\paragraph{2019}
\begin{itemize}
\itemsep0em
\item Integrate more product categories such as digital collectibles
\item Integrate stablecoin into ecosystem
\item Integrate auction, lottery and other pricing models
\item Integrate transparent voting mechanism
\item Refine user interface and overall experiences
\item Expand business partnership and onboard more celebrities to become global platform
\end{itemize}
\paragraph{2020}
\begin{itemize}
\itemsep0em
\item Expand to cover other industries such as consumer brand and general businesses
\item Work with regulatory body to create a framework to issue security tokens and allow individuals to hold crowdfunding (subject to shifting regulatory landscape)
\end{itemize}

\newpage
